---
title: "Dreams in the Mind & Spirit Project"
subtitle: Rachel E. Smith, Kara Weisman, ... & Tanya Marie Luhrmann
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include = F}
knitr::opts_chunk$set(message = F, warning = FALSE, include = F)
```

```{r, message = F}
source("../scripts_general/dependencies.R")
source("../scripts_general/custom_funs.R")
source("../scripts_general/var_recode_contrast.R")
source("../scripts_general/data_load.R")
```

# Study 1

In Study 1, adults with strong religious commitments and faith practices were interviewed in depth about their spiritual experiences and their understanding of the mind by experienced ethnographers. The "Spiritual Curiosity" interview included one question about experiencing God* through dreams (`godviadreams`) and one question about experiencing sleep paralysis (`sleepparalysis`).

```{r, include = T}
d1 %>% 
  distinct(study, researcher, country, site, religion, subject_id,
           godviadreams, sleepparalysis) %>%
  gather(question, response, c(godviadreams, sleepparalysis)) %>%
  mutate(response = factor(response, 
                           exclude = NULL,
                           levels = c(NA, 0, 0.5, 1),
                           labels = c("NA", "no", "maybe", "yes"))) %>%
  ggplot(aes(x = country, fill = country, alpha = response)) +
  facet_grid(~ recode_factor(question,
                             "godviadreams" = "dreams",
                             "sleepparalysis" = "sleep paralysis")) +
  geom_bar(stat = "count", position = "fill", color = "black", size = 0.2) +
  geom_text(data = . %>%
              count(country, question, response) %>%
              complete(response, nesting(country, question), 
                       fill = list(n = 0)) %>%
              group_by(country, question) %>%
              mutate(prop = n/sum(n)) %>%
              filter(response == "yes") %>%
              select(country, question, prop),
            aes(label = paste0(round(prop, 2)*100, "%"),
                y = prop, alpha = NULL, fill = NULL),
            color = "black", nudge_y = -0.05, size = 3, show.legend = F) +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_alpha_manual(values = c(0, 0.2, 0.4, 0.8)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_minimal() +
  guides(fill = guide_none(),
         alpha = guide_legend("Response")) +
  labs(title = "Study 1 (Spiritual Curiosity Interview)",
       x = "Country", y = "Percent of participants")
```

```{r, fig.width = 4, fig.asp = 1.2, include = T}
d1 %>% 
  distinct(study, researcher, country, site, religion, subject_id,
           godviadreams, sleepparalysis) %>%
  gather(question, response, c(godviadreams, sleepparalysis)) %>%
  mutate(response = factor(response, 
                           exclude = NULL,
                           levels = c(NA, 0, 0.5, 1),
                           labels = c("NA", "no", "maybe", "yes"))) %>%
  ggplot(aes(x = country, fill = country, alpha = response)) +
  facet_grid(interaction(site, religion, sep = " ") ~ 
               recode_factor(question,
                             "godviadreams" = "dreams",
                             "sleepparalysis" = "sleep paralysis")) +
  geom_bar(stat = "count", position = "fill", color = "black", size = 0.2) +
  geom_text(data = . %>%
              filter(!is.na(response)) %>%
              count(country, site, religion, question),
            aes(label = paste0("n=", n),
                y = 1.1, alpha = NULL, fill = NULL),
            color = "black", size = 3, show.legend = F) +
  geom_text(data = . %>%
              count(country, site, religion, question, response) %>%
              complete(response, nesting(country, site, religion, question), 
                       fill = list(n = 0)) %>%
              group_by(country, site, religion, question) %>%
              mutate(prop = n/sum(n)) %>%
              filter(response == "yes") %>%
              select(country, site, religion, question, prop),
            aes(label = paste0(round(prop, 2)*100, "%"),
                y = prop, alpha = NULL, fill = NULL),
            color = "black", nudge_y = -0.05, size = 3, show.legend = F) +
  scale_y_continuous(labels = scales::label_percent(), breaks = seq(0, 1, 0.25)) +
  scale_alpha_manual(values = c(0, 0.2, 0.4, 0.8)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_minimal() +
  guides(fill = guide_none(),
         alpha = guide_legend("Response")) +
  labs(title = "Study 1 (Spiritual Curiosity Interview)",
       x = "Country", y = "Percent of participants")
```

```{r}
r1_godviadreams <- glm(godviadreams ~ country,
                       d1 %>% 
                         distinct(study, researcher, country, site, religion, 
                                  subject_id, godviadreams) %>%
                         mutate(godviadreams = case_when(godviadreams > 0 ~ 1,
                                                         TRUE ~ godviadreams)),
                       family = "binomial")

parameters(r1_godviadreams)
```

```{r}
r1_sleepparalysis <- glm(sleepparalysis ~ country,
                       d1 %>% 
                         distinct(study, researcher, country, site, religion, 
                                  subject_id, sleepparalysis) %>%
                         mutate(sleepparalysis = case_when(sleepparalysis > 0 ~ 1,
                                                         TRUE ~ sleepparalysis)),
                       family = "binomial")

parameters(r1_sleepparalysis)
```


\newpage
# Study 2

In Study 2, adults from the general population, as well as a smaller sample of charismatic evangelical Christians, were interviewed briefly about their spiritual experiences and their understanding of the mind. As part of the "Spiritual Events" scale, these interviews included 1 question about dreams ("Some people say that the divine or supernatural sends them dreams. Has that happened to you?, `epi_2_02`) and 1 question about sleep paralysis ("Some people have had the experience of waking up but being unable to move [this is sometimes called sleep paralysis]. Has this ever happened to you?", `epi_2_20`).

```{r, include = T}
d2 %>% 
  distinct(country, epi_subj, question, response, question_text) %>%
  filter(question %in% c("epi_2_02", "epi_2_20")) %>%
  mutate(response = factor(response, 
                           exclude = NULL,
                           levels = c(NA, 0, 0.5, 1),
                           labels = c("NA", "no", "maybe", "yes"))) %>%
  ggplot(aes(x = country, fill = country, alpha = response)) +
  facet_grid(~ recode_factor(question,
                             "epi_2_02" = "dreams",
                             "epi_2_20" = "sleep paralysis")) +
  geom_bar(stat = "count", position = "fill", color = "black", size = 0.2) +
  geom_text(data = . %>%
              count(country, question, question_text, response) %>%
              complete(response, nesting(country, question, question_text), 
                       fill = list(n = 0)) %>%
              group_by(country, question, question_text) %>%
              mutate(prop = n/sum(n)) %>%
              filter(response == "yes") %>%
              select(country, question, question_text, prop),
            aes(label = paste0(round(prop, 2)*100, "%"),
                y = prop, alpha = NULL, fill = NULL),
            color = "black", nudge_y = -0.05, size = 3, show.legend = F) +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_alpha_manual(values = c(0, 0.2, 0.4, 0.8)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_minimal() +
  guides(fill = guide_none(),
         alpha = guide_legend("Response")) +
  labs(title = "Study 2 (Spiritual Epidemiology)",
       x = "Country", y = "Percent of participants")
```
```{r, fig.width = 4, fig.asp = 1, include = T}
d2 %>% 
  left_join(d2_scored %>% distinct(subject_id, religion) %>%
              rename(epi_subj = subject_id)) %>%
  distinct(country, religion, epi_subj, question, response, question_text) %>%
  filter(question %in% c("epi_2_02", "epi_2_20")) %>%
  mutate(response = factor(response, 
                           exclude = NULL,
                           levels = c(NA, 0, 0.5, 1),
                           labels = c("NA", "no", "maybe", "yes"))) %>%
  ggplot(aes(x = country, fill = country, alpha = response)) +
  facet_grid(religion ~ recode_factor(question,
                                      "epi_2_02" = "dreams",
                                      "epi_2_20" = "sleep paralysis")) +
  geom_bar(stat = "count", position = "fill", color = "black", size = 0.2) +
  geom_text(data = . %>%
              filter(!is.na(response)) %>%
              count(country, religion, question),
            aes(label = paste0("n=", n),
                y = 1.1, alpha = NULL, fill = NULL),
            color = "black", size = 3, show.legend = F) +
  geom_text(data = . %>%
              count(country, religion, question, question_text, response) %>%
              complete(response, nesting(country, religion, question, question_text), 
                       fill = list(n = 0)) %>%
              group_by(country, religion, question, question_text) %>%
              mutate(prop = n/sum(n)) %>%
              filter(response == "yes") %>%
              select(country, religion, question, question_text, prop),
            aes(label = paste0(round(prop, 2)*100, "%"),
                y = prop, alpha = NULL, fill = NULL),
            color = "black", nudge_y = -0.05, size = 3, show.legend = F) +
  scale_y_continuous(labels = scales::label_percent(), breaks = seq(0, 1, 0.25)) +
  scale_alpha_manual(values = c(0, 0.2, 0.4, 0.8)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_minimal() +
  guides(fill = guide_none(),
         alpha = guide_legend("Response")) +
  labs(title = "Study 2 (Spiritual Epidemiology)",
       x = "Country", y = "Percent of participants")
```

```{r}
r1_epi_2_02 <- glm(response ~ country,
                   d2 %>% 
                     filter(question == "epi_2_02") %>%
                     distinct(country, epi_subj, response) %>%
                     mutate(response = case_when(response > 0 ~ 1,
                                                 TRUE ~ response)),
                   family = "binomial")

parameters(r1_epi_2_02)
```

```{r}
r1_epi_2_20 <- glm(response ~ country,
                       d2 %>% 
                     filter(question == "epi_2_20") %>%
                     distinct(country, epi_subj, response) %>%
                     mutate(response = case_when(response > 0 ~ 1,
                                                 TRUE ~ response)),
                   family = "binomial")

parameters(r1_epi_2_20)
```


\newpage
# Study 3

In Study 3, college undergraduates completed a survey consisting of one measure of absorption and two measures of spiritual experience (a “Spiritual Events” inventory based on Studies 1 and 2; and a modified version of the Daily Spiritual Experiences scale). As part of the "Spiritual Events" scale, these interviews included 1 question about dreams ("Have you ever had a dream you felt was sent by God or a spirit?", `spev_09`) and 1 question about sleep paralysis ("Have you ever had the experience of being awake but unable to move?", `spev_18`).

```{r, include = T}
d3 %>% 
  distinct(country, subj, question, response) %>%
  filter(question %in% c("spev_09", "spev_18")) %>%
  mutate(response = factor(response, 
                           exclude = NULL,
                           levels = c(NA, 0, 1, 2, 3, 4),
                           labels = c("NA", "never", "once",
                                      "several times", "fairly often",
                                      "very often"))) %>%
  ggplot(aes(x = country, fill = country, alpha = response)) +
  facet_grid(~ recode_factor(question,
                             "spev_09" = "dreams",
                             "spev_18" = "sleep paralysis")) +
  geom_bar(stat = "count", position = "fill", color = "black", size = 0.2) +
  geom_text(data = . %>%
              mutate(response = case_when(
                       response %in% c("once", "several times",
                                       "fairly often", "very often") ~ 1,
                       response == "never" ~ 0,
                       TRUE ~ NA_real_)) %>%
              count(country, question, response) %>%
              complete(response, nesting(country, question),
                       fill = list(n = 0)) %>%
              group_by(country, question) %>%
              mutate(prop = n/sum(n)) %>%
              filter(response == 1) %>%
              select(country, question, prop),
            aes(label = paste0(round(prop, 2)*100, "%"),
                y = prop, alpha = NULL, fill = NULL),
            color = "black", nudge_y = -0.05, size = 3, show.legend = F) +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_alpha_manual(values = c(0, 0.1, 0.5, 0.6, 0.7, 0.8, 0.9)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_minimal() +
  guides(fill = guide_none(),
         alpha = guide_legend("Response")) +
  labs(title = "Study 3 (Packet 1)",
       x = "Country", y = "Percent of participants")
```

```{r}
r1_spev_09 <- clm(response ~ country,
                  data = d3 %>% 
                    filter(question == "spev_09") %>%
                    distinct(country, subj, response) %>%
                    mutate(response = factor(response)))

parameters(r1_spev_09)
```

```{r}
r1_spev_18 <- clm(response ~ country,
                  data = d3 %>% 
                    filter(question == "spev_18") %>%
                    distinct(country, subj, response) %>%
                    mutate(response = factor(response)))

parameters(r1_spev_18)
```


\newpage
# Study 4

In Study 4, college undergraduates completed a survey consisting of nine measures, including two indices of porosity, the Absorption scale, two indices of spiritual experience, two indices of more secular extraordinary experience, and two control measures. As part of the "Spiritual Events" scale, this packet included 1 question about dreams ("Have you ever had a dream you felt was sent by God or a spirit?", `p7_se_dream.sent`) and 1 question about sleep paralysis ("Have you ever had the experience of being awake but unable to move?", `p7_se_slep.paralysis`).

As part of the "Paranormal" scale, this packet also included 1 additional question about dreams ("I am completely convinced that I [have never had a/have had at least one] dream that came true and which (I believe) was not just a coincidence."; `p7_exsen_dream.true`).

```{r, include = T}
d4 %>% 
  select(country, p7_subj, 
         p7_se_dream.sent, p7_se_slep.paralysis) %>%
  gather(question, response, 
         c(p7_se_dream.sent, p7_se_slep.paralysis)) %>%
  distinct(country, p7_subj, question, response) %>%
  mutate(response = factor(response, 
                           exclude = NULL,
                           levels = c(NA, 0, 1, 2, 3, 4),
                           labels = c("NA", "never", "once",
                                      "several times", "fairly often",
                                      "very often"))) %>%
  ggplot(aes(x = country, fill = country, alpha = response)) +
  facet_grid(~ recode_factor(question,
                             "p7_se_dream.sent" = "dreams",
                             "p7_se_slep.paralysis" = "sleep paralysis",
                             "p7_exsen_dream.true" = "dream come true")) +
  geom_bar(stat = "count", position = "fill", color = "black", size = 0.2) +
  geom_text(data = . %>%
              mutate(response = case_when(
                       response %in% c("once", "several times",
                                       "fairly often", "very often") ~ 1,
                       response == "never" ~ 0,
                       TRUE ~ NA_real_)) %>%
              count(country, question, response) %>%
              complete(response, nesting(country, question),
                       fill = list(n = 0)) %>%
              group_by(country, question) %>%
              mutate(prop = n/sum(n)) %>%
              filter(response == 1) %>%
              select(country, question, prop),
            aes(label = paste0(round(prop, 2)*100, "%"),
                y = prop, alpha = NULL, fill = NULL),
            color = "black", nudge_y = -0.05, size = 3, show.legend = F) +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_alpha_manual(values = c(0, 0.1, 0.5, 0.6, 0.7, 0.8, 0.9)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_minimal() +
  guides(fill = guide_none(),
         alpha = guide_legend("Response")) +
  labs(title = "Study 4 (Packet 7)",
       x = "Country", y = "Percent of participants")
```

```{r, include = T}
d4 %>% 
  select(country, p7_subj, p7_exsen_dream.true) %>%
  gather(question, response, c(p7_exsen_dream.true)) %>%
  distinct(country, p7_subj, question, response) %>%
  mutate(response = factor(response, 
                           exclude = NULL,
                           levels = c(NA, 0, 1),
                           labels = c("NA", "no", "yes"))) %>%
  ggplot(aes(x = country, fill = country, alpha = response)) +
  facet_grid(~ recode_factor(question,
                             "p7_se_dream.sent" = "dreams",
                             "p7_se_slep.paralysis" = "sleep paralysis",
                             "p7_exsen_dream.true" = "dream come true")) +
  geom_bar(stat = "count", position = "fill", color = "black", size = 0.2) +
  geom_text(data = . %>%
              count(country, question, response) %>%
              complete(response, nesting(country, question),
                       fill = list(n = 0)) %>%
              group_by(country, question) %>%
              mutate(prop = n/sum(n)) %>%
              filter(response == "yes") %>%
              select(country, question, prop),
            aes(label = paste0(round(prop, 2)*100, "%"),
                y = prop, alpha = NULL, fill = NULL),
            color = "black", nudge_y = -0.05, size = 3, show.legend = F) +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_alpha_manual(values = c(0, 0.2, 0.8)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_minimal() +
  guides(fill = guide_none(),
         alpha = guide_legend("Response")) +
  labs(title = "Study 4 (Packet 7)",
       x = "Country", y = "Percent of participants")
```

```{r}
library(ordinal)
```

```{r}
r1_p7_se_dream.sent <- clm(p7_se_dream.sent ~ country,
                           data = d4 %>% 
                             distinct(country, p7_subj, p7_se_dream.sent) %>%
                             mutate(p7_se_dream.sent = factor(p7_se_dream.sent)))

parameters(r1_p7_se_dream.sent)
```

```{r}
r1_p7_se_slep.paralysis <- clm(p7_se_slep.paralysis ~ country,
                           data = d4 %>% 
                             distinct(country, p7_subj, p7_se_slep.paralysis) %>%
                             mutate(p7_se_slep.paralysis = factor(p7_se_slep.paralysis)))

parameters(r1_p7_se_slep.paralysis)
```

```{r}
r1_p7_exsen_dream.true <- glm(p7_exsen_dream.true ~ country,
                              d4 %>% 
                                distinct(p7_subj, country, p7_exsen_dream.true),
                              family = "binomial")

parameters(r1_p7_exsen_dream.true)
```


\newpage
# Studies 1-4: God* via dreams

```{r}
g1 <- d1 %>% 
  distinct(study, researcher, country, site, religion, subject_id, godviadreams) %>%
  gather(question, response, c(godviadreams)) %>%
  mutate(response = factor(response, 
                           exclude = NULL,
                           levels = c(NA, 0, 0.5, 1),
                           labels = c("NA", "no", "maybe", "yes"))) %>%
  ggplot(aes(x = country, fill = country, alpha = response)) +
  facet_grid(~ recode_factor(question,
                             "godviadreams" = "dreams",
                             "sleepparalysis" = "sleep paralysis")) +
  geom_bar(stat = "count", position = "fill", color = "black", size = 0.2) +
  geom_text(data = . %>%
              count(country, question, response) %>%
              complete(response, nesting(country, question), 
                       fill = list(n = 0)) %>%
              group_by(country, question) %>%
              mutate(prop = n/sum(n)) %>%
              filter(response == "yes") %>%
              select(country, question, prop),
            aes(label = paste0(round(prop, 2)*100, "%"),
                y = prop, alpha = NULL, fill = NULL),
            color = "black", nudge_y = -0.05, size = 3, show.legend = F) +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_alpha_manual(values = c(0, 0.2, 0.8)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_minimal() +
  guides(fill = guide_none(),
         alpha = guide_legend("Response")) +
  labs(title = "Study 1",
       x = "Country", y = "Percent of participants")
```

```{r}
g2 <- d2 %>% 
  distinct(country, epi_subj, question, response, question_text) %>%
  filter(question %in% c("epi_2_02")) %>%
  mutate(response = factor(response, 
                           exclude = NULL,
                           levels = c(NA, 0, 0.5, 1),
                           labels = c("NA", "no", "maybe", "yes"))) %>%
  ggplot(aes(x = country, fill = country, alpha = response)) +
  facet_grid(~ recode_factor(question,
                             "epi_2_02" = "dreams",
                             "epi_2_20" = "sleep paralysis")) +
  geom_bar(stat = "count", position = "fill", color = "black", size = 0.2) +
  geom_text(data = . %>%
              count(country, question, question_text, response) %>%
              complete(response, nesting(country, question, question_text), 
                       fill = list(n = 0)) %>%
              group_by(country, question, question_text) %>%
              mutate(prop = n/sum(n)) %>%
              filter(response == "yes") %>%
              select(country, question, question_text, prop),
            aes(label = paste0(round(prop, 2)*100, "%"),
                y = prop, alpha = NULL, fill = NULL),
            color = "black", nudge_y = -0.05, size = 3, show.legend = F) +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_alpha_manual(values = c(0, 0.2, 0.4, 0.8)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_minimal() +
  guides(fill = guide_none(),
         alpha = guide_legend("Response")) +
  labs(title = "Study 2",
       x = "Country", y = "Percent of participants")
```

```{r}
g3 <- d3 %>% 
  distinct(country, subj, question, response) %>%
  filter(question %in% c("spev_09")) %>%
  mutate(response = factor(response, 
                           exclude = NULL,
                           levels = c(NA, 0, 1, 2, 3, 4),
                           labels = c("NA", "never", "once",
                                      "several times", "fairly often",
                                      "very often"))) %>%
  ggplot(aes(x = country, fill = country, alpha = response)) +
  facet_grid(~ recode_factor(question,
                             "spev_09" = "dreams",
                             "spev_18" = "sleep paralysis")) +
  geom_bar(stat = "count", position = "fill", color = "black", size = 0.2) +
  geom_text(data = . %>%
              mutate(response = case_when(
                       response %in% c("once", "several times",
                                       "fairly often", "very often") ~ 1,
                       response == "never" ~ 0,
                       TRUE ~ NA_real_)) %>%
              count(country, question, response) %>%
              complete(response, nesting(country, question),
                       fill = list(n = 0)) %>%
              group_by(country, question) %>%
              mutate(prop = n/sum(n)) %>%
              filter(response == 1) %>%
              select(country, question, prop),
            aes(label = paste0(round(prop, 2)*100, "%"),
                y = prop, alpha = NULL, fill = NULL),
            color = "black", nudge_y = -0.05, size = 3, show.legend = F) +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_alpha_manual(values = c(0, 0.1, 0.5, 0.6, 0.7, 0.8, 0.9)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_minimal() +
  guides(fill = guide_none(),
         alpha = guide_legend("Response")) +
  labs(title = "Study 3",
       x = "Country", y = "Percent of participants")
```

```{r}
g4 <- d4 %>% 
  select(country, p7_subj, p7_se_dream.sent) %>%
  gather(question, response, c(p7_se_dream.sent)) %>%
  distinct(country, p7_subj, question, response) %>%
  mutate(response = factor(response, 
                           exclude = NULL,
                           levels = c(NA, 0, 1, 2, 3, 4),
                           labels = c("NA", "never", "once",
                                      "several times", "fairly often",
                                      "very often"))) %>%
  ggplot(aes(x = country, fill = country, alpha = response)) +
  facet_grid(~ recode_factor(question,
                             "p7_se_dream.sent" = "dreams",
                             "p7_se_slep.paralysis" = "sleep paralysis",
                             "p7_exsen_dream.true" = "dream come true")) +
  geom_bar(stat = "count", position = "fill", color = "black", size = 0.2) +
  geom_text(data = . %>%
              mutate(response = case_when(
                       response %in% c("once", "several times",
                                       "fairly often", "very often") ~ 1,
                       response == "never" ~ 0,
                       TRUE ~ NA_real_)) %>%
              count(country, question, response) %>%
              complete(response, nesting(country, question),
                       fill = list(n = 0)) %>%
              group_by(country, question) %>%
              mutate(prop = n/sum(n)) %>%
              filter(response == 1) %>%
              select(country, question, prop),
            aes(label = paste0(round(prop, 2)*100, "%"),
                y = prop, alpha = NULL, fill = NULL),
            color = "black", nudge_y = -0.05, size = 3, show.legend = F) +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_alpha_manual(values = c(0, 0.1, 0.5, 0.6, 0.7, 0.8, 0.9)) +
  scale_fill_brewer(palette = "Dark2") +
  theme_minimal() +
  guides(fill = guide_none(),
         alpha = guide_legend("Response")) +
  labs(title = "Study 4",
       x = "Country", y = "Percent of participants")
```

```{r, fig.width = 6, fig.asp = 0.4, include = T}
plot_grid(g1 + 
            labs(x = NULL) +
            guides(alpha = guide_none()) + 
            theme(strip.text = element_blank()), 
          g2 + 
            labs(x = NULL, y = NULL) +
            guides(alpha = guide_none()) + 
            theme(strip.text = element_blank(),
                  axis.text.y = element_blank()), 
          g3 + 
            labs(x = NULL, y = NULL) +
            guides(alpha = guide_none()) + 
            theme(strip.text = element_blank(),
                  axis.text.y = element_blank()), 
          g4 + 
            labs(x = NULL, y = NULL) +
            guides(alpha = guide_none()) + 
            theme(strip.text = element_blank(),
                  axis.text.y = element_blank()), 
          nrow = 1, rel_widths = c(1, rep(0.85, 3)))
```


\newpage
# Demographics 

## Study 1 (Luhrmann, Weisman, et al., 2020, _PNAS_: Table S14)

```{r}
d1_demo <- d1_scored %>% select(-contains("score")) %>% 
  mutate(male = ifelse(grepl("male", tolower(subject_gender)) &
                         !grepl("female", tolower(subject_gender)), 1, 0),
         female = ifelse(grepl("female", tolower(subject_gender)), 1, 0),
         subject_age = ifelse(subject_age > 120, NA_real_, subject_age),
         subject_hs = ifelse(grepl("yes", tolower(subject_hs)), 1, 0))
```

```{r, include = T}
d1_demo %>%
  filter(!is.na(country), !is.na(site), !is.na(religion)) %>%
  mutate(site = factor(site, levels = c("urban", "rural"))) %>%
  group_by(country, site, religion) %>%
  summarise(n = n(),
            age_range = paste0(min(subject_age, na.rm = T), "-",
                               max(subject_age, na.rm = T)),
            mean_age = mean(subject_age, na.rm = T),
            percent_male = mean(male, na.rm = T),
            percent_female = mean(female, na.rm = T),
            percent_hs = mean(subject_hs, na.rm = T),
            percent_special = mean(subject_specialrole, na.rm = T)) %>%
  ungroup() %>%
  # mutate_at(vars(starts_with("mean_")), funs(format(round(., 2), nsmall = 2))) %>%
  mutate_at(vars(starts_with("percent_")),
            funs(paste0(round(. * 100), "%"))) %>%
  rename(Country = country, Site = site, Religion = religion,
         `Age range` = age_range, `Mean age` = mean_age,
         `% male` = percent_male, `% female` = percent_female,
         `% attended high school` = percent_hs,
         `% serving a 'special role'` = percent_special) %>%
  kable(digits = 2, align = c(rep("l", 3), rep("r", 4))) %>%
  kable_styling(font_size = 16) # %>%
# collapse_rows(1:2)
```


\newpage
## Study 2 (Luhrmann, Weisman, et al., 2020, _PNAS_: Table S15)

```{r}
d2_demo <- d2_scored %>% select(-contains("score")) %>% 
  mutate(male = ifelse(grepl("male", tolower(subject_gender)) &
                         !grepl("female", tolower(subject_gender)), 1, 0),
         female = ifelse(grepl("female", tolower(subject_gender)), 1, 0),
         subject_age = ifelse(subject_age > 120, NA_real_, subject_age),
         # deal with subject_religion
         subject_religion = case_when(
           subject_religion %in% 
             c("7th Day Adventist",
               "A little Catholicism, pray Jesus",
               "Apostolic",
               "Baptist",
               "Catholic",
               "Catholic 5 times a year, don't study bible but large part of family make up.",
               "Catholicism",
               "Christian",
               "Christian Baptist",
               "Christian, raised Catholic",
               "christianity",
               "Christianity",
               "Christianity - possibly Presbyterian / Catholic, Raised Pentecostal",
               "Christianity, nondenominational",
               "Christians",
               "Christiantity",
               "Church of Latter Day Saints",
               "Culturally LDS",
               "Episcopalian",
               "Grew up Catholic",
               "ICGC Cape Coast Branch, Christianity",
               "Jehovah Witness", 
               "Jehovah's Witness",
               "LDS Latter Day Saints",
               "Methodist",
               "non denominational / Christian",
               "non-denominational",
               "Not specific type/denomination, parents bounced around, all Christian",
               "Orthodox Christian", "Pentecostal", "Pentecostal preacher",
               "Personal relationship w/ Jesus Christ", "Presbyterian",
               "Roman Catholic", "SDA (Christianity)",
               "Seventh Day Adventist Church", "True Jesus Church",
               "Unitarian Universalism", "United Methodist") ~ "Christian",
           subject_religion %in% 
             c("Actually believe in Buddhism",
               "Buddhism", "Buddhism (believe)",
               "Buddhism / Ancestors (a little bit believe)",
               "Buddhism, incline to deism",
               "Buddhism. Practice and has been vegetarian for 20 years",
               "Buddhist",
               "Buddhist (interviewed @ church)",
               "Incline to Buddhism", "Studying Buddhism",
               "Vipassana Buddhism",
               "Wat Baan Pong Kiang",
               "Wat Hua Deng", 
               "Wat Nong Ban") ~ "Buddhist",
           # subject_religion %in% 
           #   c("Family - Orthodox Jew / Jewish",
           #     "Judaism", "Orthodox Jewish") ~ "Jewish",
           subject_religion %in%
             c("Islam", 
               "Islam, but not believe anything", 
               "Islamic", 
               "Islamic Religion",
               "Muslim") ~ "Muslim",
           # subject_religion %in% 
           #   c("Hinduism") ~ "Hindu",
           grepl("agnost", tolower(subject_religion)) |
             grepl("atheis", tolower(subject_religion)) |
             grepl("don't", tolower(subject_religion)) |
             grepl("none", tolower(subject_religion)) |
             tolower(subject_religion) %in% 
             c("n/a", "no", 
               tolower("No (ex - JW) Partner Christian - Possibly Korean Baptist"), 
               "no religion", "no religion, finding one", "not really",
               tolower("Religion is a choice; I'm not interested in it.")) ~ "Agnostic/Atheist",
           subject_religion %in% c("missing data", "mdata", "NA") |
             is.na(subject_religion) ~ "Missing data",
           TRUE ~ "Other"),
         subject_urban_rural = recode(subject_urban_rural,
                                      "Urban" = 1, "Rural" = 0),
         religion = recode_factor(religion,
                                  "0" = "general pop.",
                                  "1" = "charismatic Chr."),
         agnostic_atheist = (subject_religion == "Agnostic/Atheist"),
         buddhist = (subject_religion == "Buddhist"),
         christian = (subject_religion == "Christian"),
         muslim = (subject_religion == "Muslim"),
         other = (subject_religion == "Other"),
         missing = (subject_religion == "Missing data"))
```

```{r, include = T}
d2_demo %>%
  group_by(country, religion) %>%
  summarise(n = n(),
            age_range = paste0(min(subject_age, na.rm = T), "-",
                               max(subject_age, na.rm = T)),
            mean_age = mean(subject_age, na.rm = T),
            percent_male = mean(male, na.rm = T),
            percent_female = mean(female, na.rm = T),
            percent_urban = mean(subject_urban_rural, na.rm = T),
            percent_affr = mean(subject_afford, na.rm = T),
            mean_ses = mean(subject_ses, na.rm = T),
            mean_religiosity = mean(subject_religiosity, na.rm = T),
            percent_christian = mean(christian, na.rm = T),
            percent_agnostic_atheist = mean(agnostic_atheist, na.rm = T),
            percent_buddhist = mean(buddhist, na.rm = T),
            percent_muslim = mean(muslim, na.rm = T),
            percent_other = mean(other, na.rm = T),
            percent_missing = mean(missing, na.rm = T)) %>%
  ungroup() %>%
  # mutate_at(vars(starts_with("mean_")), funs(format(round(., 2), nsmall = 2))) %>%
  mutate_at(vars(starts_with("percent_")),
            funs(paste0(round(. * 100), "%"))) %>%
  rename(Country = country, Sample = religion,
         `Age range` = age_range, `Mean age` = mean_age,
         `% male` = percent_male, `% female` = percent_female,
         `% urban` = percent_urban, `% can afford` = percent_affr,
         `Mean SES` = mean_ses, `Mean religiosity` = mean_religiosity,
         `% Christian` = percent_christian, 
         `% Agnostic/Atheist` = percent_agnostic_atheist, 
         `% Buddhist` = percent_buddhist, 
         `% Muslim` = percent_muslim, 
         `% Other` = percent_other,
         `[% Missing data]` = percent_missing) %>%
  mutate(Country = factor(Country, levels = levels_country),
         Sample = factor(Sample, 
                         levels = c("general population", "charismatic"),
                         labels = c("gen. pop.", "char. ev. Chr."))) %>%
  arrange(Country, Sample) %>%
  select(Country, Sample, n, `Age range`, `Mean age`, `% male`, `% female`,
         `Mean religiosity`,
         `% Christian`, `% Buddhist`, `% Muslim`, `% Other`, `% Agnostic/Atheist`,
         `[% Missing data]`,
         `% urban`, `% can afford`, `Mean SES`) %>%
  kable(digits = 2, align = c(rep("l", 2), rep("r", ncol(.) - 2))) %>%
  kable_styling(font_size = 16) # %>%
# collapse_rows(1:2)
```


\newpage
## Study 3 (Luhrmann, Weisman, et al., 2020, _PNAS_: Table S16)

```{r}
d3_demo <- d3_scored %>% select(-contains("score")) %>% 
  mutate(male = ifelse(grepl("male", tolower(subject_gender)) &
                         !grepl("female", tolower(subject_gender)), 1, 0),
         female = ifelse(grepl("female", tolower(subject_gender)), 1, 0),
         subject_age = ifelse(subject_age > 120, NA_real_, subject_age),
         subject_religion = case_when(
           subject_religion %in% 
             c("christian", "(seventh day adventist) youth", "a.o.g.", "anglican",
               "anglicanism", "aog", "aog assemblies of god", 
               "agos, assemblies of god", "assemblies of god",
               "c.m.c presbyterian", "christian - ame (google it!)",
               "christian: anglican", "christian: catholic", 
               "christian: non specific", "christian: non-specific",
               "christian: protestant mainline", "christianity",
               "christianity: non specific", "church of christ",
               "coptic orthodox christian",
               "family worship ark healing ministry",
               "kingdom citizenship of god", "living water", "ntm",
               "pentecostal", "presbyterian", "presbyterian (illegible)",
               "protestant", "s.d.a.", "sda", "sda (seventh day adventist)",
               "seven day adventist", "seventh day adventist", 
               "seventh day adventist church", "sunday keeper",
               "word christian fellowship") ~ "Christian",
           subject_religion %in% 
             c("buddhist", "dge-lugs-pa (buddhist sect)", "sanqi buddhism",
               "some values of buddhism", "buddha temple", "buddha temples",
               "buddha temples & ancestral hall", "buddhist temples") ~ "Buddhist",
           # subject_religion %in% 
           #   c("Family - Orthodox Jew / Jewish",
           #     "Judaism", "Orthodox Jewish") ~ "Jewish",
           subject_religion %in%
             c("muslim") ~ "Muslim",
           # subject_religion %in% 
           #   c("Hinduism") ~ "Hindu",
           grepl("agnost", tolower(subject_religion)) |
             grepl("atheis", tolower(subject_religion)) |
             grepl("don't", tolower(subject_religion)) |
             grepl("none", tolower(subject_religion)) |
             tolower(subject_religion) %in% 
             c("n/a", "no", "no religion", "not really") ~ "Agnostic/Atheist",
           subject_religion %in% c("missing data", "mdata", "NA") |
             is.na(subject_religion) ~ "Missing data",
           TRUE ~ "Other"),
         agnostic_atheist = (subject_religion == "Agnostic/Atheist"),
           buddhist = (subject_religion == "Buddhist"),
           christian = (subject_religion == "Christian"),
           muslim = (subject_religion == "Muslim"),
           other = (subject_religion == "Other"),
         missing = (subject_religion == "Missing data"))
```

```{r, include = T}
d3_demo %>%
  group_by(country) %>%
  summarise(n = n(),
            age_range = paste0(min(subject_age, na.rm = T), "-",
                               max(subject_age, na.rm = T)),
            mean_age = mean(subject_age, na.rm = T),
            percent_male = mean(male, na.rm = T),
            percent_female = mean(female, na.rm = T),
            percent_affr = mean(subject_afford, na.rm = T),
            mean_ses = mean(subject_ses, na.rm = T),
            mean_religiosity = mean(subject_religiosity, na.rm = T),
            percent_christian = mean(christian, na.rm = T),
            percent_agnostic_atheist = mean(agnostic_atheist, na.rm = T),
            percent_buddhist = mean(buddhist, na.rm = T),
            percent_muslim = mean(muslim, na.rm = T),
            percent_other = mean(other, na.rm = T),
            percent_missing = mean(missing, na.rm = T)) %>%
  ungroup() %>%
  # mutate_at(vars(starts_with("mean_")), funs(format(round(., 2), nsmall = 2))) %>%
  mutate_at(vars(starts_with("percent_")),
            funs(paste0(round(. * 100), "%"))) %>%
  rename(Country = country, 
         `Age range` = age_range, `Mean age` = mean_age,
         `% male` = percent_male, `% female` = percent_female,
         `% can afford` = percent_affr,
         `% Christian` = percent_christian, 
         `% Agnostic/Atheist` = percent_agnostic_atheist, 
         `% Buddhist` = percent_buddhist, 
         `% Muslim` = percent_muslim, 
         `% Other` = percent_other,
         `[% Missing data]` = percent_missing,
         `Mean SES` = mean_ses, `Mean religiosity` = mean_religiosity) %>%
  mutate(Country = factor(Country, levels = levels_country)) %>%
  arrange(Country) %>%
  select(Country, n, `Age range`, `Mean age`, `% male`, `% female`,
         `Mean religiosity`,
         `% Christian`, `% Buddhist`, `% Muslim`, `% Other`, `% Agnostic/Atheist`,
         `[% Missing data]`,
         `% can afford`, `Mean SES`) %>%
  kable(digits = 2, align = c(rep("l", 2), rep("r", ncol(.) - 2))) %>%
  kable_styling(font_size = 16) # %>%
# collapse_rows(1:2)
```


\newpage
## Study 4 (Luhrmann, Weisman, et al., 2020, _PNAS_: Table S17)

```{r}
d4_demo <- d4_scored %>% select(-contains("score")) %>% 
  mutate(male = ifelse(grepl("male", tolower(subject_gender)) &
                         !grepl("female", tolower(subject_gender)), 1, 0),
         female = ifelse(grepl("female", tolower(subject_gender)), 1, 0),
         subject_age = ifelse(subject_age > 120, NA_real_, subject_age),
         urban = ifelse(subject_urban_rural == "urban", 1, 0),
         subject_religion = case_when( # deal with religion
           subject_religion %in% 
             c("A.O.G.", "Anglican", "AoG", "AOG", "AOG (Assembly of God)",
               "Apostolic Life Ministry", "Assemblies of God", "Assemblies of God (AOG)",
               "Baptism", "Bible Church", "Bible Church of Vanuatu", "catholic",
               "Catholic", "catholicism", "Catholicism", "Catholicism / Christianism",
               "Chirstianity", "Christian", "Christian Mission Center",
               "Christian religion", "Christianianity", "christianity",
               "Christianity", "Church of Christ", "CMC", "CMC Church", "COC",
               "Living Water [Fresh waters]", "Living Wota (Freshwotas)", "Methodist",
               "New Governant Church of Vanuatu", "NTM", "only Christian",
               "Only Christian", "Only Christian!", "Pilow of Five Ministry",
               "Praise & Worship", "Presbyterian", "Roman Catholic", "S.D.A",
               "S.D.A. Youth", "Sabbath", "SDA (Saturday)", "SDA (Seventh Day Adventist)",
               "SDA, Seventh Day Adventist", "Seventh Day Adventist", "Sunday",
               "Sunday worship", "Sunday Worship", 
               "The Church of Jesus Christ of Latter Day Saints",
               "United Methodist Christian") ~ "Christian",
           subject_religion %in% 
             c("Buddhist", "Buddhism") ~ "Buddhist",
           subject_religion %in%
             c("Muslim", "Islam", "Islam / Mohammedanism", "Islam/Mohammedanism",
               "Some Islam habits") ~ "Muslim",
           grepl("agnost", tolower(subject_religion)) |
             grepl("atheis", tolower(subject_religion)) |
             grepl("don't", tolower(subject_religion)) |
             grepl("none", tolower(subject_religion)) |
             subject_religion == "." | is.na(subject_religion) |
             tolower(subject_religion) %in% 
             c("n/a", "no", "no religion", 
               "no religion, finding one", "not really") ~ "Agnostic/Atheist",
           subject_religion %in% c("missing data", "mdata", "NA") |
             is.na(subject_religion) ~ "Missing data",
           TRUE ~ "Other"),
         agnostic_atheist = (subject_religion == "Agnostic/Atheist"),
         buddhist = (subject_religion == "Buddhist"),
         christian = (subject_religion == "Christian"),
         muslim = (subject_religion == "Muslim"),
         other = (subject_religion == "Other"),
         missing = (subject_religion == "Missing data"))
```

```{r, include = T}
d4_demo %>%
  group_by(country) %>%
  summarise(n = n(),
            age_range = paste0(min(subject_age, na.rm = T), "-",
                               max(subject_age, na.rm = T)),
            mean_age = mean(subject_age, na.rm = T),
            percent_male = mean(male, na.rm = T),
            percent_female = mean(female, na.rm = T),
            percent_urban = mean(urban, na.rm = T),
            percent_affr = mean(subject_afford, na.rm = T),
            mean_ses = mean(subject_ses, na.rm = T),
            mean_religiosity = mean(subject_religiosity, na.rm = T),
            percent_christian = mean(christian, na.rm = T),
            percent_agnostic_atheist = mean(agnostic_atheist, na.rm = T),
            percent_buddhist = mean(buddhist, na.rm = T),
            percent_muslim = mean(muslim, na.rm = T),
            percent_other = mean(other, na.rm = T),
            percent_missing = mean(missing, na.rm = T)) %>%
  ungroup() %>%
  # mutate_at(vars(starts_with("mean_")), funs(format(round(., 2), nsmall = 2))) %>%
  mutate_at(vars(starts_with("percent_")),
            funs(paste0(round(. * 100), "%"))) %>%
  rename(Country = country, 
         `Age range` = age_range, `Mean age` = mean_age,
         `% male` = percent_male, `% female` = percent_female,
         `% urban` = percent_urban, `% can afford` = percent_affr,
         `Mean SES` = mean_ses, `Mean religiosity` = mean_religiosity,
         `% Christian` = percent_christian, 
         `% Agnostic/Atheist` = percent_agnostic_atheist, 
         `% Buddhist` = percent_buddhist, 
         `% Muslim` = percent_muslim, 
         `% Other` = percent_other,
         `[% Missing data]` = percent_missing) %>%
  mutate(Country = factor(Country, levels = levels_country)) %>%
  arrange(Country) %>%
  select(Country, n, `Age range`, `Mean age`, `% male`, `% female`,
         `Mean religiosity`,
         `% Christian`, `% Buddhist`, `% Muslim`, `% Other`, `% Agnostic/Atheist`,
         `[% Missing data]`,
         `% urban`, `% can afford`, `Mean SES`) %>%
  kable(digits = 2, align = c(rep("l", 2), rep("r", ncol(.) - 2))) %>%
  kable_styling(font_size = 16) # %>%
# collapse_rows(1:2)
```

